MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-02-11 MAESTROeX_I/paper.tex
more simplifications.  need to discuss etarho and psi

@@

Call {\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, p_0^n] \rightarrow [\rho^{(1)},(\rho h)^{(1)},X_k^{(1)},T^{(1)},(\rho \omegadot_k)^{(1)},(\rho \Hnuc)^{(1)}]$.
\MarginPar{AJN: I think we can simplify the description here... this is somewhat confusing now.}

@@

Using the equation below,
%
\begin{equation}
\frac{\partial\Ub}{\partial t} = -\Ub\cdot\nabla\Ub - \frac{1}{\rho}\nabla\pi - \frac{\rho-\rho_0}{\rho}g\eb_r, \label{eq:u_update}
\end{equation}
%
we compute time-centered edge velocities, $\uadvonedag$, using
$\Ub^n$.  The $\dagger$ superscript refers to the
fact that the predicted velocity field does not satisfy the divergence
constraint.  We then construct $\uadvone$ from $\uadvonedag$
using a MAC projection.
We note that $\uadvone$ satisfies the divergence constraint
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = \beta_0^n \left(S^{\nph,\star} - \frac{1}{\overline{\Gamma}_1^np_0^n}\psi^{n-\myhalf} + \chi^n \right),
\end{equation}
\begin{equation}
 \beta_0^n = \beta_0 \left(\rho_0^n, p_0^n, \overline{\Gamma}_1^n\right),
\end{equation}
\begin{equation}
\chi^n = \frac{f}{\overline{\Gamma}_1^n p_0^n}\frac{p_{\rm eos}^n(\rho,h,X_k) - p_0^n}{\Delta t^n}
\end{equation}
where $\beta_0$ is computed as described in Appendix C of Paper III.

@@

Call {\bf React State}$[ \rho^{(2),\star},(\rho h)^{(2),\star}, X_k^{(2),\star}, T^{(2),\star}, p_0^{n+1,\star}]$\\
\phantom{ }\hfill $\rightarrow [ \rho^{n+1,\star},(\rho h)^{n+1,\star}, X_k^{n+1,\star}, T^{n+1,\star}, (\rho \omegadot_k)^{(2),\star}, (\rho \Hnuc)^{(2),\star} ].$

@@

The procedure to construct $\uadvtwodag$ is identical to the procedure
for computing $\uadvonedag$ in {\bf Step 3}, but uses
the updated value $S^{\nph}$ rather than $S^{\nph,\star}$.
Also, the temporal changes of $p_0$ are now computed directly instead of 
approximated using $\psi$.
We note that $\uadvtwo$ satisfies the divergence constraint
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \uadvtwo\right) =
\beta_0^{\nph} \left(S^{\nph} - \frac{1}{\overline{\Gamma}_1^{n+\myhalf}p_0^{n+1,\star}}\frac{p_0^{n+1,\star}-p_0^n}{\Delta t^n} + \chi^{n+\myhalf}\right),
\end{equation}
\begin{equation}
\beta_0^{\nph} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2};
\qquad
 \beta_0^{n+1,\star} = \beta_0 \left(\rho_0^{n+1,\star}, p_0^{n+1,\star}, \overline{\Gamma}_1^{n+1,\star}\right),
\end{equation}
\begin{equation}
\overline{\Gamma}_1^{\nph} = \frac{ \overline{\Gamma}_1^n +  \overline{\Gamma}_1^{n+1,\star} }{2}.
\end{equation}
\begin{equation}
\chi^{n+\myhalf} = \chi^n + \frac{f}{\overline{\Gamma}_1^{n+1,\star} p_0^{n+1,\star}}\frac{p_{\rm eos}^{n+1,\star}(\rho,h,X_k) - p_0^{n+1,\star}}{\Delta t^n}
\end{equation}

@@

Call {\bf React State}$[\rho^{(2)},(\rho h)^{(2)}, X_k^{(2)},T^{(2)}, p_0^{n+1}] \rightarrow [\rho^{n+1}, (\rho h)^{n+1}, X_k^{n+1}, T^{n+1}, (\rho \omegadot_k)^{(2)}, (\rho \Hnuc)^{(2)} ].$

@@

First, we compute the time-centered edge velocities, $\Ub^{\nph,\pred}$.
Then, we define
\begin{equation}
\rho^\nph = \frac{\rho^n + \rho^{n+1}}{2}, \qquad \rho_0^\nph = \frac{\rho_0^n + \rho_0^{n+1}}{2}.
\end{equation}
We update the velocity field $\Ub^n$ to $\Ub^{n+1,\dagger}$ by discretizing
equation (\ref{eq:u_update}) as
\begin{eqnarray}
\Ub^{n+1,\dagger}
&=& \Ub^n - \dt \left[\uadvtwo \cdot \nabla \Ub^{\nph,\pred} \right] \nonumber \\
&& - \dt \left[ \frac{1}{\rho^\nph} \mathbf{G} \pi^\nmh + \frac{\left(\rho^\nph-\rho_0^\nph\right)}{\rho^\nph} g^{\nph} \eb_r \right],\nonumber \\
\end{eqnarray}
where $\mathbf{G}$ approximates a cell-centered gradient from nodal
data.  Again, the $\dagger$ superscript refers
to the fact that the updated velocity does not satisfy the divergence
constraint.

>>>>

\MarginPar{AJN: eliminated references to volume discrepancy for now; we'd only use it for planar at the moment, don't want to open up that can of worms here}

@@

Call {\bf React State}$[(\rho X_k)^n, (\rho h)^n, p_0^n] \rightarrow [(\rho X_k)^{(1)}, (\rho h)^{(1)}, (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)}]$.
\MarginPar{AJN: I think we can simplify the description here... this is somewhat confusing now.}

@@

Using equation (\ref{eq:momentum}), 
we compute time-centered edge velocities, $\uadvonedag$, using
$\Ub^n$.  The $\dagger$ superscript refers to the
fact that the predicted velocity field does not satisfy the divergence
constraint.  We then construct $\uadvone$ from $\uadvonedag$
using a MAC projection.
We note that $\uadvone$ satisfies the divergence constraint
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = \beta_0^n \left(S^{\nph,\star} - \frac{1}{\overline{\Gamma}_1^np_0^n}\psi^{n-\myhalf} \right),
\end{equation}
\begin{equation}
 \beta_0^n = \beta_0 \left(\rho_0^n, p_0^n, \overline{\Gamma}_1^n\right),
\end{equation}
where $\beta_0$ is computed as described in Appendix C of Paper III.

@@

Call {\bf React State}$[ (\rho X_k)^{(2),\star}, (\rho h)^{(2),\star}, p_0^{n+1,\star}]$\\
\phantom{ }\hfill $\rightarrow [ (\rho X_k)^{n+1,\star}, (\rho h)^{n+1,\star}, (\rho \omegadot_k)^{(2),\star}, (\rho \Hnuc)^{(2),\star} ].$

@@

The procedure to construct $\uadvtwodag$ is identical to the procedure
for computing $\uadvonedag$ in {\bf Step 3}, but uses
the updated value $S^{\nph}$ rather than $S^{\nph,\star}$.
Also, the temporal changes of $p_0$ are now computed directly instead of 
approximated using $\psi$.
We note that $\uadvtwo$ satisfies the divergence constraint
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \uadvtwo\right) =
\beta_0^{\nph} \left(S^{\nph} - \frac{1}{\overline{\Gamma}_1^{n+\myhalf}p_0^{n+1,\star}}\frac{p_0^{n+1,\star}-p_0^n}{\Delta t^n}\right),
\end{equation}
\begin{equation}
\beta_0^{\nph} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2};
\qquad
 \beta_0^{n+1,\star} = \beta_0 \left(\rho_0^{n+1,\star}, p_0^{n+1,\star}, \overline{\Gamma}_1^{n+1,\star}\right),
\end{equation}
\begin{equation}
\overline{\Gamma}_1^{\nph} = \frac{ \overline{\Gamma}_1^n +  \overline{\Gamma}_1^{n+1,\star} }{2}.
\end{equation}

@@

Call {\bf React State}$[(\rho X_k)^{(2)},(\rho h)^{(2)}, p_0^{n+1}] \rightarrow [(\rho X_k)^{n+1}, (\rho h)^{n+1}, (\rho \omegadot_k)^{(2)}, (\rho \Hnuc)^{(2)}].$

@@

First, we compute the time-centered edge velocities, $\Ub^{\nph,\pred}$.
Then, we define
\begin{equation}
\rho^\nph = \frac{\rho^n + \rho^{n+1}}{2}, \qquad \rho_0^\nph = \frac{\rho_0^n + \rho_0^{n+1}}{2}.
\end{equation}
We update the velocity field $\Ub^n$ to $\Ub^{n+1,\dagger}$ by discretizing
equation (\ref{eq:momentum}) as
\begin{eqnarray}
\Ub^{n+1,\dagger}
&=& \Ub^n - \dt \left[\uadvtwo \cdot \nabla \Ub^{\nph,\pred} \right] \nonumber \\
&& - \dt \left[ \frac{1}{\rho^\nph} \mathbf{G} \pi^\nmh + \frac{\left(\rho^\nph-\rho_0^\nph\right)}{\rho^\nph} g^{\nph} \eb_r \right],\nonumber \\
\end{eqnarray}
where $\mathbf{G}$ approximates a cell-centered gradient from nodal
data.  Again, the $\dagger$ superscript refers
to the fact that the updated velocity does not satisfy the divergence
constraint.
